---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# erosivity

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/kvantas/erosivity?branch=master&svg=true)](https://ci.appveyor.com/project/kvantas/erosivity)
[![Travis-CI Build Status](https://travis-ci.org/kvantas/erosivity.svg?branch=master)](https://travis-ci.org/kvantas/erosivity)
[![codecov](https://codecov.io/github/kvantas/erosivity/branch/master/graphs/badge.svg)](https://codecov.io/gh/kvantas/erosivity) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-6666ff.svg)](https://cran.r-project.org/)
[![packageversion](https://img.shields.io/badge/Package%20version-0.0.9000-orange.svg?style=flat-square)](https://github.com/kvantas/erosivity)

The goal of `erosivity` is to compute the rainfall erosivity using precipitation data.


## Installation

You can install the development version from GitHub with:

```{r github_install, eval = FALSE}
# install.packages("devtools")
devtools::install_github("kvantas/erosivity")
```

## Using erosivity

## Example

## Meta

* Please report any [issues or bugs](https://github.com/kvantas/hydroscoper/issues).

* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.


## References

 1. Renard, K. G., Foster, G. R., Weesies, G. A. and Porter, J. P. (1991), ‘RUSLE: Revised Universal Soil Loss Equation’, *Journal of Soil and Water Conservation* **46**(1), 30–33.

