---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# erosivity

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/kvantas/erosivity?branch=master&svg=true)](https://ci.appveyor.com/project/kvantas/erosivity)
[![Travis-CI Build Status](https://travis-ci.org/kvantas/erosivity.svg?branch=master)](https://travis-ci.org/kvantas/erosivity)
[![codecov](https://codecov.io/github/kvantas/erosivity/branch/master/graphs/badge.svg)](https://codecov.io/gh/kvantas/erosivity) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-6666ff.svg)](https://cran.r-project.org/)
[![packageversion](https://img.shields.io/badge/Package%20version-0.0.9000-orange.svg?style=flat-square)](https://github.com/kvantas/erosivity)

The goal of `erosivity` is to compute the rainfall erosivity using precipitation data.


## Installation

You can install the development version from GitHub with:

```{r github_install, eval = FALSE}
# install.packages("devtools")
devtools::install_github("kvantas/erosivity")
```

## Erosivity calculation

The R coefficient (MJ.mm/ha/h/yr) is defined as the long-term average of the product of the kinetic energy of a storm and the maximum 30 min intensity (Renard et. al, 1987):

$$R = \frac{1}{n} \sum_{j=1}^{n} \sum_{k=1}^{m_j} (EI_{30})_{k}$$

where $n$ is the number of years with rainfall records, $m_j$ the number of storms during year $j$ and $EI_{30}$
the erosivity of storm $k$. The erosivity $EI_{30}$ (MJ.mm/ha/h) is equal to:

$$EI_{30} = \left( \sum_{r=1}^{m} e_r \cdot v_{r} \right) \cdot I_{30}$$

where $e_r$ is the energy of rainfall (MJ/ha/mm), $v_r$ the rainfall depth (mm) for the time interval $r$ of the hyetograph, which has been divided into $r = 1, 2, ..., m$ sub-intervals, such that each one of these is characterized by constant rainfall intensity and $I_{30}$ is the maximum rainfall intensity for a 30 minutes duration. The quantity $e_r$ is calculated for $r$ from the relation:

$$e_{r} = 0.29 \left( 1 - 0.72 e^{-0.05 \cdot i_{r}} \right)$$

where $i_r$ is the rainfall intensity (mm/h). The rules that apply in order to single out the storms causing erosion and to divide rainfalls of large duration are:

1. A rainfall event is divided into two parts, if its cumulative depth for duration of 6 hours at a certain location is less than 1.3 mm.
2. A rainfall is considered erosive:
   * if it has a cumulative value greater than 12.7 mm or
   * during a time period of 15 mins a cumulative value of at least 6.4 mm is recorded.

## Using erosivity

## Example

## Meta

* Please report any [issues or bugs](https://github.com/kvantas/hydroscoper/issues).

* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.


## References

 1. Renard, K. G., Foster, G. R., Weesies, G. A. and Porter, J. P. (1991), ‘RUSLE: Revised Universal Soil Loss Equation’, *Journal of Soil and Water Conservation* **46**(1), 30–33.

